---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# emberr

<!-- badges: start -->

[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental) [![R-CMD-check](https://github.com/andypicke/emberr/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/andypicke/emberr/actions/workflows/R-CMD-check.yaml)

<!-- badges: end -->

The goal of emberr is to provide functions to query and retrieve data from the [Ember](https://ember-climate.org/) [API](https://ember-climate.org/data/api/).

You can view the [API documentation](https://api.ember-climate.org/docs) for details. Please note the license information provided by Ember:

*Our data is published using the CC-BY-4.0 license. Anyone is able to use our data for any purpose (personal, commercial, etc.). The only requirements by this license are that:

1) Ember is cited as the data source. E.g. 'Monthly electricity generation data, Ember'
2) You may not add any additional legal/technological restrictions to the data.*

## Installation

You can install the development version of emberr from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("andypicke/emberr")
```

You will need to sign up for a free API key.

The package assumes you have stored your API key in your .Renviron file as *EMBER_API_KEY*

## Example

Get monthly electiricty generation data for 2021-2023:
```{r example}
library(emberr)

gen <- emberr::get_electricity_generation(temporal_resolution = "monthly", min_date = 2021, max_date = 2023)

head(gen)

```

Get options for *entity* parameter

```{r}

options <- emberr::get_ember_options(dataset = "electricity-generation", filter_name = "entity")

str(options)

```

