---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# emberr

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental) [![R-CMD-check](https://github.com/andypicke/emberr/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/andypicke/emberr/actions/workflows/R-CMD-check.yaml)
[![Project Status: WIP](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
<!-- badges: end -->

The goal of {emberr} is to provide functions to query and retrieve data from the [Ember](https://ember-energy.org/) [API](https://ember-energy.org/data/api/).

You can view the [API documentation](https://api.ember-energy.org/docs) for details. Please note the license information provided by Ember:

*Our data is published using the CC-BY-4.0 license. Anyone is able to use our data for any purpose (personal, commercial, etc.). The only requirements by this license are that:

1) Ember is cited as the data source. E.g. 'Monthly electricity generation data, Ember'
2) You may not add any additional legal/technological restrictions to the data.*

See this [blog post](https://andypicke.quarto.pub/portfolio/posts/emberr/emberr.html) for a description and examples of the package.

## Installation

You can install the development version of [emberr](https://github.com/andypicke/emberr) from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("andypicke/emberr")
```

You will need to sign up for a free API key from Ember.

The package assumes you have stored your API key in your .Renviron file as *EMBER_API_KEY*. You can also pass in an API key explicitly to each function.

## Using the package

The main function to retrieve a dataset from the api is *get_ember_data()*.

There are 4 main datasets available from the API (these correspond to the *dataset* option in *get_ember_data()*:
- electricity-generation
- power-sector-emissions
- electricity-demand
- carbon-intensity

Each dataset is available in yearly or monthly resolution (the *temporal_resolution* option in *get_ember_data()*).

Countries/regions are contained in the *entity* variable. 

## Example

Get monthly electricity generation data for 2021-2023. By Default this returns data for all countries/regions ("entities").
```{r example}
library(emberr)

gen <- emberr::get_ember_data(dataset = "electricity-generation", 
                              temporal_resolution = "monthly", 
                              min_date = 2021, 
                              max_date = 2023)

head(gen)

```

The *series* variable specifies the fuel type:
```{r}
unique(gen$series)
```


You can specify a single year instead of a min and max date:
```{r}

gen_2023 <- emberr::get_ember_data(dataset = "electricity-generation", 
                              temporal_resolution = "monthly", 
                              year = 2023)

head(gen_2023)
```

The *get_ember_options()* function can be used to return all options for a variable. For example, get options for the *entity* parameter:

```{r}

options <- emberr::get_ember_options(dataset = "electricity-generation", filter_name = "entity")

str(options)

```

or the *series* parameter:
```{r}

options_series <- emberr::get_ember_options(dataset = "electricity-generation", filter_name = "series")

options_series

```


Retrieve data for just one country/region by specifying an entity:

```{r}

df_usa <- emberr::get_ember_data(entity = "United States")

str(df_usa)

```


You can also retrieve data for multiple countries/regions (entities) by passing a comma-separated list:

```{r}

df <- get_ember_data(min_date = 2020, entity = "United States,United Kingdom")
str(df)

```


